DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-01 ase2017/paper.tex
reviewed conclusions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\tool can synthesize digital controllers for dynamic physical plants, 
represented in MATLAB as a transfer function or a state-space model,  
w.r.t. stability and safety, using the CEGIS approach. 
%
Given the current literature in controller synthesis, there is no other MATLAB toolbox 
for synthesizing stable digital controllers for physical plants, while taking into account all aspects of its digital implementation (fixed-point arithmetic). 
%
As future work, \tool will perform synthesis of other types of specifications (e.g., performance) 
and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 
other controller properties (e.g., presence of limit cycles).

>>>>

\tool can automatically synthesize stable digital controllers for intricate dynamic physical plants, 
represented in MATLAB as a transfer function or a state-space equation using the CEGIS approach. 
In particular, the \tool represents the first fully automated synthesis
tool that is algorithmically and numerically sound, considering various error
sources in the implementation of the digital control algorithm and in the computational 
modeling of plant dynamics~\cite{abate2017,abatecav2017}.
%
Additionally, given the current literature in controller synthesis, there is no other MATLAB toolbox 
for synthesizing stable digital controllers for physical plants, while taking into account all aspects of its 
digital implementation. 
%
As future work, the \tool will perform synthesis of other specifications (e.g., performance) 
and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 
other controller properties (e.g., presence of limit cycles).
